### 2015-11-23 Irregular-occ/Irregular-occ.tex
.

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          L. Beauvalet
          \inst{2},
          R. Vieira-Martins
          \inst{1,2,3} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
%          J.-E. Arlot
%          \inst{4},      
          J. I. B. Camargo
          \inst{2,3},     
          B. E. Morgado
          \inst{1,2}
%          F. Braga-Ribas
%          \inst{2,4}, 
%          D. N. da Silva Neto
%          \inst{6},
%          A. H. Andrei
%          \inst{1,2} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau, 75014 Paris, France},
%          A. Dias-Oliveira
%          \inst{2},
%          G. Benedetti-Rossi
%          \inst{2},
%          Y. Duchemin
%          \inst{4,7},
%          J. Desmars
%          \inst{4},
%          V. Lainey
%          \inst{4},
%          W. Thuillot
%          \inst{4}
          }

@@

   \institute{Observatório do Valongo/UFRJ, Ladeira Pedro Antônio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
              \email{altair08@astro.ufrj.br}
              \and
Observatório Nacional/MCT, R. General José Cristino 77,
CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
              \email{rvm@on.br}
              \and
Laboratório Interinstitucional de e-Astronomia - LIneA, Rua Gal. José Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil
%              \and
%Institut de mécanique céleste et de calcul des éphémérides - Observatoire %de Paris, UMR 8028 du CNRS,
%77 Av. Denfert-Rochereau, 75014 Paris, France\\
%              \email{arlot@imcce.fr}
%              \and
%Federal University of Technology - Paraná (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
%              \and
%Centro Universitário Estadual da Zona Oeste, Av. Manual Caldeira de Alvarenga 1203, CEP 23.070-200 Rio de Janeiro RJ, Brazil
%              \and
%              ESIGELEC-IRSEEM, Technopôle du Madrillet, Avenue Galilée, 76801 Saint-Etienne du Rouvray, France
              }

@@

ARG-J thanks the financial support of CAPES. MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013). RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj/PAPDRJ-45/2013. JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6). FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014. BEM thanks the financial support of CAPES.

>>>>

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          L. Beauvalet
          \inst{2,3},
          R. Vieira-Martins
          \inst{1,2,4} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
%          J.-E. Arlot
%          \inst{4},      
          J. I. B. Camargo
          \inst{2,4},     
          B. E. Morgado
          \inst{1,2}
%          F. Braga-Ribas
%          \inst{2,4}, 
%          D. N. da Silva Neto
%          \inst{6},
%          A. H. Andrei
%          \inst{1,2} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau, 75014 Paris, France},
%          A. Dias-Oliveira
%          \inst{2},
%          G. Benedetti-Rossi
%          \inst{2},
%          Y. Duchemin
%          \inst{4,7},
%          J. Desmars
%          \inst{4},
%          V. Lainey
%          \inst{4},
%          W. Thuillot
%          \inst{4}
          }

@@

   \institute{Observatório do Valongo/UFRJ, Ladeira Pedro Antônio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
              \email{altair08@astro.ufrj.br}
              \and
Observatório Nacional/MCT, R. General José Cristino 77,
CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
              \email{rvm@on.br}
              \and
Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France
              \and
Laboratório Interinstitucional de e-Astronomia - LIneA, Rua Gal. José Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil
%              \and
%Institut de mécanique céleste et de calcul des éphémérides - Observatoire %de Paris, UMR 8028 du CNRS,
%77 Av. Denfert-Rochereau, 75014 Paris, France\\
%              \email{arlot@imcce.fr}
%              \and
%Federal University of Technology - Paraná (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
%              \and
%Centro Universitário Estadual da Zona Oeste, Av. Manual Caldeira de Alvarenga 1203, CEP 23.070-200 Rio de Janeiro RJ, Brazil
%              \and
%              ESIGELEC-IRSEEM, Technopôle du Madrillet, Avenue Galilée, 76801 Saint-Etienne du Rouvray, France
              }

@@

ARG-J thanks the financial support of CAPES.
MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013).
RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj/PAPDRJ-45/2013.
JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6).
%FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014.
BEM thanks the financial support of CAPES.
The numerical model of the satellites of Jupiter was developped during a post-doctoral contract funded by the Chinese Academy of Sciences (CAS) and supported by the National Scientific Fund of China (NSFC)
